\chapter*{Publications}
\addcontentsline{toc}{chapter}{Publications}

\vspace{1em}

\noindent\textbf{\textit{Journal international à comité de lecture}}

\vspace{0.5em}

\noindent \underline{Oger, A.}, Gorisse, G., Fleury, S. et Christmann, O. (2025). MemorIA, an Architecture for Creating Interactive AI Historical Agents in Educational Contexts. \textit{Computer Animation and Virtual Worlds}, 36(3). DOI~: 10.1002/cav.70032.

\vspace{1.5em}

\noindent\textbf{\textit{Articles soumis à des journaux internationaux à comité de lecture}}

\vspace{0.5em}

\noindent \underline{Oger, A.}, Gorisse, G., Fleury, S., Bondesan, P. et Christmann, O. (2025). The Influence of AI-Based Virtual Agents' Interactivity and Representation on Secondary School Students' Interest in History. Soumis à \textit{International Journal of Child-Computer Interaction}.

\vspace{0.5em}

\noindent \underline{Oger, A.}, Gorisse, G., Fleury, S. et Christmann, O. (2025). Study of the Influence of AI-Powered Virtual Agent Design on the Illusion of Understanding in Middle School Students. Soumis à \textit{Journal of Computer Assisted Learning}.

\vspace{1.5em}

\noindent\textbf{\textit{Communication en conférence internationale}}

\vspace{0.5em}

\noindent \underline{Oger, A.}, Gorisse, G., Fleury, S. et Christmann, O. (2025). MemorIA, an Architecture for Creating Interactive AI Historical Agents in Educational Contexts. Communication présentée au \textit{38th Computer Animation and Social Agents (CASA 2025)}, Strasbourg, France, 2--4 juin 2025.

\cleardoublepage
